Papers

### 2025-01-16 papers.qmd
fix paper
add arxiv

## 2025

## 2024
K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2024.

N. Winovich, Nick, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.

J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024. [arxiv preprint](https://arxiv.org/abs/2409.13938)

>>>>

## 2025
K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Computational Statistics and Data Analysis*, submitted, 2025. [arxiv preprint](https://arxiv.org/abs/2501.07602)

N. Winovich, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, in revision, 2024.

## 2024
J. E. Borgert, J. Hannig, **J. D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J. S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024. [arxiv preprint](https://arxiv.org/abs/2409.13938)
